### 2018-04-04 Sections/economics_of_the_quantum_internet.tex
Finished economics table

This parameter acts as an overall, network size-dependent price scaling factor on:
\begin{itemize}
\item Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}).
\item Time-share spot price (Sec.~\ref{sec:time_share_spot}).
\item Computational dividend (Sec.~\ref{sec:comp_div}).
\item Qubit asset price (Sec.~\ref{sec:qubit_pricing_model}).
\item Forward contracts (Sec.~\ref{sec:for_contr}).
\end{itemize}

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=0.47\textwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.\comment{Colours are fucked.}} \label{fig:NPSF}
\end{figure}

@@

% Efficient Markets
%

@@

\subsection{Network power}

@@

\begin{postulate}[Network power]\label{post:network_power}\index{Network power}
The combined computational power of the entire network, measured in FLOPS, is given by,
\begin{align}
n_\text{FLOPS}(t) &= f_\text{sc}(n_\text{global})\nonumber \\
&= f_\text{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

@@

\begin{postulate}[Network value]\label{post:network_value}\index{Network value}
The dollar-value of the entire network is given by,
\begin{align}
	P_t &= C_t N_t \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

@@

Let $L_t$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time, per FLOP is,
\begin{align}\index{Cost of computation postulate}
	L_t &= \frac{e^{-\gamma_\text{ror}} P_t}{n_\text{FLOPS}(t)} \nonumber\\
	&= \frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)},
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L_0 = \frac{e^{-\gamma_\text{ror}}C_0}{\chi_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-sharing}, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.

The net computing power\index{Time-shared compute-time} allocated to the node is then given by,
\begin{align}
	c_n &= r_n \cdot f_\text{sc}(n_\text{global}) \nonumber \\
	&= n \cdot \chi_\text{sc}(n_\text{global})
\end{align}
\end{definition}

@@

The key observation is that a unit of computation (FLOP) does not carry over time. It must be utilised immediately and cannot be stored for future use. This simplifies the forward price of a unit of computation to simply be the future spot price, discounted by the risk-free RoR, yielding the forward contract pricing model for quantum computing time-shares,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in qubits is,
\begin{align}
F_T &= e^{-r_\text{rf}T} L_T\nonumber\\
&=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}
\end{align}
\end{definition}

@@

Using our illustrative examples of computational scaling functions (linear, polynomial and exponential), the respective tax performance multipliers are given by,
\begin{align}
M_\text{linear}(N_\text{tax}) &= {\gamma_T}^{-1}, \nonumber \\
M_\text{poly}(N_\text{tax}) &= {\gamma_T}^{-p}, \nonumber \\
M_\text{exp}(N_\text{tax}) &= e^{N_\text{tax}(1-\gamma_T)}.
\end{align}

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset (Sec.~\ref{sec:qubit_pricing_model}), future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their RoI will reflect these market dynamics.

@@

What makes a sound currency\index{Sound currency}? First of all, it must exhibit scarcity\index{Scarcity} and be difficult or impossible to counterfeit\index{Counterfeit} -- it should not be possible to forge unlimited quantities out of thin air, a quality not inherent to fiat currency. Second, its abundance should exhibit relative stablility and predictability over time, so as to create a stable money supply\index{Money supply}. For these reasons, gold for thousands of years was accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as they exhibit these same traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

@@

Time-shares in unified computing power over the quantum network, via licensing out qubits from hardware owners, would provide all these essential desired qualities of a sound currency. It can be envisaged that forward contracts in compute-time (Sec.~\ref{sec:for_contr}) would act as a good basis for backing a currency. Since these are simple paper contracts, they lend themselves to highly fluid, low-overhead trading on international markets.

@@

\textit{--- \href{https://www.youtube.com/watch?v=lhyaiOZhpSg}{End the Fed.}}

%
% Summary
%

\subsection{Summary}

@@

\begin{table*}[!htb]
\caption{Summary of the dynamics of various economic models under several computational scaling functions of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network.\comment{Complete}} \label{tab:summary_ec_models}
\begin{tabular}{|p{0.255\linewidth}|p{0.22\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|p{0.155\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n^{}\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	Network price scaling factor (Sec.~\ref{sec:NPSF}) & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	Spot price of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_0=\frac{e^{-\gamma_\text{ror}} C_0}{\chi_\text{sc}(N_0)}\] & &  & \\
	\hline
	Future cost of computation (Sec.~\ref{sec:cost_of_comp}) & \[L_t=\frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)}
\] &  &  & \\
	\hline
	Time-share computational power (Sec.~\ref{sec:arb_free_time_share}) & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	Single qubit leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev}) & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n e^{N_0{\gamma_N}^t-n}}{N_0{\gamma_N}^t}\]\\
	\hline
	Forward contract price (Sec.~\ref{sec:for_contr}) & \[F_T=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}\]
 &  & & \\
	\hline
	Tax performance multiplier (Sec.~\ref{sec:taxation}) & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[{\gamma_T}^{-1}\] & \[{\gamma_T}^{-p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\end{table*}

>>>>

This parameter acts as an overall, network size-dependent price scaling factor on:
\begin{itemize}
\item Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}).
\item Cost of computation (Sec.~\ref{sec:cost_of_comp}).
\item Time-shared computational power (Sec.~\ref{sec:arb_free_time_share}).
\item Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev}).
\item Forward contracts (Sec.~\ref{sec:for_contr}).
\end{itemize}

@@

\begin{figure}[htb!]\index{Network price scaling factor}
	\includegraphics[width=0.47\textwidth]{network_price_scaling_factor}
	\caption{Scaling of the network price scaling factor, $\chi_\text{sc}$, as a function of several representative computational scaling functions, $f_\text{sc}$, where $n$ is network size.} \label{fig:NPSF}
\end{figure}

@@

%
% Efficient Markets
%

@@

\subsection{Network power}\index{Network power}\label{sec:network_power}

@@

\begin{postulate}[Network power]\label{post:network_power}\index{Network power}
The combined computational power of the entire network, measured in FLOPS, is given by,
\begin{align}
P(t) &= f_\text{sc}(n_\text{global})\nonumber \\
&= f_\text{sc}(N_0{\gamma_N}^t).
\end{align}
\end{postulate}

@@

\begin{postulate}[Network value]\label{post:network_value}\index{Network value}
The dollar-value of the entire network is given by,
\begin{align}
	V(t) &= C_t N_t \nonumber \\
	&= C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t.
\end{align}
\end{postulate}

@@

Let $L_t$ be the dollar-value of utilising the network's computing resources for a single unit of time. This is obtained as the return made on the value of the network per FLOP,
\begin{postulate}[Cost of computation]\label{post:cost_comp}
The efficient-market dollar-value of a computation for a single unit of time, per FLOP is,
\begin{align}\index{Cost of computation postulate}
	L(t) &= \frac{e^{-\gamma_\text{ror}} P_t}{V_t} \nonumber\\
	&= \frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)},
\end{align}
\end{postulate}
which implies,
\begin{postulate}[Spot price of computation]\index{Spot price of computation} The present-day (\mbox{$t=0$}) spot price of a computation per FLOP is,
\begin{align}
L(0) = \frac{e^{-\gamma_\text{ror}}C_0}{\chi_\text{sc}(N_0)}.	
\end{align}
\end{postulate}
That is, the value of computations simply approximates the return on initial hardware investment, scaled by its initial computational power, as is intuitively expected.

@@

Additionally, we have assumed no compute-cycles are wasted -- compute-time is always fully utilised, as per Pos.~\ref{post:market_eff}. Then it follows that the time-share of the combined resources of the entire network should be unity,
\begin{align}
	r_{n_\text{global}}=1.
\end{align}
\mbox{$r_{n_\text{global}}<1$} would imply inefficiency via wasted clock-cycles. Combining this with the linearity constraint implies the arbitrage-free time-sharing model,
\begin{definition}[Arbitrage-free time-sharing model] \label{def:arb_free_ts}\index{Arbitrage-free time-sharing model}
In an efficient market for unified quantum computing time-shares\index{Time-sharing}, a network participant in possession of $n$ of the entire $n_\text{global}$ qubits in the network is entitled to the fraction of unified network compute time,
\begin{align}\index{Time-shared compute-time}
	r_n = \frac{n}{n_\text{global}},
\end{align}
where,
\begin{align}
n_\text{global} = \sum_{j\in\text{nodes}} n_j,
\end{align}
is the total number of qubits in the network, and,
\begin{align}
0\leq r_n \leq 1.	
\end{align}
\mbox{$r_n=1$} iff the node has a complete monopoly over qubits, i.e \mbox{$n=n_\text{global}$}.
\end{definition}

Based on this equitable model for time-sharing,
\begin{definition}[Time-shared computing power]\index{Time-shared computing power}
The computing power allocated to each user under the arbitrage-free time-sharing model is,
\begin{align}
	c_n &= r_n \cdot f_\text{sc}(n_\text{global}) \nonumber \\
	&= n \cdot \chi_\text{sc}(n_\text{global}).
\end{align}
\end{definition}

@@

The key observation is that a unit of computation (FLOP) does not carry over time. It must be utilised immediately and cannot be stored for future use. This simplifies the forward price of a unit of computation to simply be the future spot price, discounted by the risk-free RoR, yielding the forward contract pricing model for quantum computing time-shares,
\begin{definition}[Forward contract pricing model] \label{def:forward_cont}\index{Forward contract pricing model}
The efficient market price for a forward contract in qubits is,
\begin{align}
F(T) &= e^{-r_\text{rf}T} L(T)\nonumber\\
&=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}
\end{align}
\end{definition}

@@

Using our illustrative examples of computational scaling functions (linear, polynomial and exponential), the respective tax performance multipliers are given by,
\begin{align}
M_\text{linear}(N_\text{tax}) &= \frac{1}{\gamma_T}, \nonumber \\
M_\text{poly}(N_\text{tax}) &= \frac{1}{{\gamma_T}^p}, \nonumber \\
M_\text{exp}(N_\text{tax}) &= e^{N_\text{tax}(1-\gamma_T)}.
\end{align}

@@

What is likely to arise is that most owners of quantum hardware will not be consumers, but rather investors, who float their resources on the quantum stock market, betting on changes in demand for computation and their associated subjective cost. This trading could involve transactions in the direct underlying asset, future contracts (Sec.~\ref{sec:for_contr}) for locking in required computational power at future points in time, or more complex derivatives. For example, an investor anticipating a surge in high-value computations is likely to invest more heavily into hardware with the expectation of an uptrend in market rates. And their RoI will reflect these market dynamics.

@@

What makes a sound currency\index{Sound currency}? First of all, it must exhibit scarcity\index{Scarcity} and be difficult or impossible to counterfeit\index{Counterfeit} -- it should not be possible to forge unlimited quantities out of thin air, a quality not inherent to fiat currency. Second, its abundance and demand should exhibit relative stablility and predictability over time, so as to create a stable money supply\index{Money supply} and inflationary rate. For these reasons, gold\index{Gold standard} for thousands of years was accepted as legal tender, since it is naturally scarce and much work must be invested into its production. For the same reasons, emerging cryptocurrencies have become widely adopted and even the norm in hyper-inflating countries like Venezuela where fiat currency has lost all integrity, as they exhibit these same traits. But rather than scarcity of a natural resource, we are dealing with artificial scarcity of bit-strings, cryptographically enforced to satisfy certain mathematical properties that cannot be easily counterfeited.

@@

Time-shares in unified computing power over the quantum network, via licensing out qubits from hardware owners, would provide all these essential desired qualities of a sound currency. It can be envisaged that forward contracts in compute-time (Sec.~\ref{sec:for_contr}) would act as a good basis for backing a currency. Since these are nothing but simple forward contracts, they lend themselves to highly fluid, low-overhead trading on international markets.

@@

Unlike fiat currency, this monetary system would not be inflationary since the commodity backing the currency is one which cannot be counterfeited -- the only way to make more currency is to provide more genuine, functional, online qubits, which increases the money supply in tandem with the underlying asset backing it. This would in effect be a full-reserve banking system\index{Full-reserve banking}, where the direct one-to-one interchangeability between currency (forward contracts on computation) and it backing asset (physical qubits) eliminates the money multiplier\index{Money multiplier}, a system essentially immune to bank runs\index{Bank runs}.

Because the currency is forward contracts in computing time-shares, not ownership of the physical underlying qubits, the qubits needn't change hands upon being utilised in monetary transactions. The currency could reside entirely on a distributed digital ledger\index{Distributed ledger} recording transactions in the future contracts, independent of trading in physical qubits, who owns them, or where they reside.

In a strategically fractured world, where multiple, independent quantum internets may exist in isolation to one another, each with their own local QuantCoin\texttrademark currencies, there would be an enormous monetary incentive to breaking down trade barriers and globalising the network by unifying smaller ones. This is contrary to nationalised fiat currencies, where there is little incentive for, yet much to lose by unifying currencies. Greed on behalf of those owning QuantCoins\texttrademark would therefore directly incentivise harmony and integration amongst all the world's leading players in the technological realm, making QuantCoin\texttrademark a major driver of peace and prosperity in the quantum world of tomorrow.

Importantly, a computation-backed currency would be largely immune to political interference. Politicians would have zero ability to directly manipulate the money supply, short of suicidally self-destructive policies like shutting down or curtailing the quantum internet. Having a sound monetary system, immunised against political interference, will play an important role in constraining the power of government and extending personal liberty.

\latinquote{\href{https://www.youtube.com/watch?v=lhyaiOZhpSg}{End the Fed!} Libertas justitia veritas. Libertas perfundet omnia luce.}

%
% Summary of Economic Models
%

\subsection{Summary of economic models}

@@

\begin{table*}[!htb]
\begin{tabular}{|m{0.21\linewidth}|m{0.22\linewidth}|m{0.155\linewidth}|m{0.155\linewidth}|m{0.2\linewidth}|}
	\hline
	\[\text{Model}\] & \[\text{General form}\] & \[f_\text{sc}(n)=n\] & \[f_\text{sc}(n)=n^p\] & \[f_\text{sc}(n)=e^n\]\\
	\hline \hline
	\begin{flushleft}Network price scaling factor (Sec.~\ref{sec:NPSF})\end{flushleft} & \[\chi_\text{sc}(n)=\frac{f_\text{sc}(n)}{n}\] & \[1\] & \[n^{p-1}\] & \[\frac{e^n}{n}\]\\
	\hline
	\begin{flushleft}Network power (Sec.~\ref{sec:network_power})\end{flushleft} & \[P(t)=f_\text{sc}(N_0{\gamma_N}^t)\] & \[N_0{\gamma_N}^t\] & \[\left(N_0{\gamma_N}^t\right)^p\] & \[ e^{N_0{\gamma_N}^t}\] \\
	\hline
	\begin{flushleft}Network value (Sec.~\ref{sec:network_value})\end{flushleft} & \[V(t)=C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t\] & \[C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t\] & \[C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t\] & \[C_0 N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t\] \\
	\hline
	\begin{flushleft}Spot price of computation (Sec.~\ref{sec:cost_of_comp})\end{flushleft} & \[L(0)=\frac{e^{-\gamma_\text{ror}} C_0}{\chi_\text{sc}(N_0)}\] & \[e^{-\gamma_\text{ror}} C_0\] &  \[\frac{e^{-\gamma_\text{ror}}C_0}{{N_0}^{p-1}}\] & \[\frac{e^{-\gamma_\text{ror}}N_0C_0}{e^{N_0}}\] \\
	\hline
	\begin{flushleft}Future cost of computation (Sec.~\ref{sec:cost_of_comp})\end{flushleft} & \[L(t)=\frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{\chi_\text{sc}(N_0 {\gamma_N}^t)}
\] & \[e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t} \] & \[ \frac{e^{-\gamma_\text{ror}} C_0{\gamma_C}^{-t}}{(N_0 {\gamma_N}^t)^{p-1}}
\] & \[ \frac{e^{-\gamma_\text{ror}} C_0N_0 \left(\frac{\gamma_N}{\gamma_C}\right)^t}{e^{N_0 {\gamma_N}^t}}\] \\
	\hline
	\begin{flushleft}Time-share computational power (Sec.~\ref{sec:arb_free_time_share})\end{flushleft} & \[c_n=n \cdot \chi_\text{sc}(n_\text{global})
\] & \[n\] & \[n\cdot{n_\text{global}}^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}}\]\\
	\hline
	\begin{flushleft}Quantum computational leverage (Sec.~\ref{sec:quant_ec_lev})\end{flushleft} & \[\lambda_n=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(n)}\] & \[1\] & \[\left(\frac{n_\text{global}}{n}\right)^{p-1}\] & \[\frac{n e^{n_\text{global}}}{n_\text{global}e^n}\]\\
	\hline
	\begin{flushleft}Single-qubit leverage (Sec.~\ref{sec:quant_ec_lev})\end{flushleft} & \[\lambda_\text{qubit}=\frac{\chi_\text{sc}(n_\text{global})}{\chi_\text{sc}(1)}\] & \[1\] & \[{n_\text{global}}^{p-1}\] & \[\frac{e^{n_\text{global}-1}}{n_\text{global}}\]\\
	\hline
	\begin{flushleft}Time-dependent leverage (Sec.~\ref{sec:quant_ec_lev})\end{flushleft} & \[\lambda_n(t)=\frac{\chi_\text{sc}(N_0{\gamma_N}^t)}{\chi_\text{sc}(n)}\] &  \[1\] & \[\left(\frac{N_0{\gamma_N}^t}{n}\right)^{p-1}\] & \[\frac{n e^{N_0{\gamma_N}^t-n}}{N_0{\gamma_N}^t}\]\\
	\hline
	\begin{flushleft}Forward contract price (Sec.~\ref{sec:for_contr})\end{flushleft} & \[F(T)=\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{\chi_\text{sc}(N_0 {\gamma_N}^T)}\]
 & \[e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}\] & \[\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0{\gamma_C}^{-T}}{(N_0 {\gamma_N}^T)^{p-1}}\] & \[\frac{e^{-\gamma_\text{ror}-r_\text{rf}T} C_0N_0\left(\frac{\gamma_N}{\gamma_C}\right)^T}{e^{N_0 {\gamma_N}^T}}\] \\
	\hline
	\begin{flushleft}Tax performance multiplier (Sec.~\ref{sec:taxation})\end{flushleft} & \[M(N_\text{tax})=\frac{f_\text{sc}(N_\text{tax})}{f_\text{sc}(N_\text{tax} \gamma_T)}\] & \[\frac{1}{\gamma_T}\] & \[\frac{1}{{\gamma_T}^p}\] & \[e^{N_\text{tax}(1-\gamma_T)}\]\\
	\hline
\end{tabular}
\caption{Summary of the dynamics of various economic models under several computational scaling functions ($f_\text{sc}$) of interest, where there are $n$ qubits held by the respective node and \mbox{$n_\text{global}=\sum_{j\in \text{nodes}} n_j$} qubits in the global network. $N_0$ is the initial number of qubits, undergoing growth rate $\gamma_N$. $C_0$ is the initial monetary cost per qubit, undergoing decay rate $\gamma_C$. $\gamma_\text{ror}$ is the rate of return on the licensing of compute-time on qubits, and $r_\text{rf}$ is the risk-free rate of return. $\gamma_T$ is the rate of taxation, and $N_\text{tax}$ is the number of qubits that would exist on the network in the absence of taxation.} \label{tab:summary_ec_models}
\end{table*}

### 2018-04-04 Sections/foreword.tex
Very minor
Finished economics table

\section{Foreword}

@@

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed'.\index{Zed}}, and classical networking \cite{bib:TanenbaumNet} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

@@

The theme music for this work may be found \href{http://soundcloud.com/peter-rohde/wir-sind-ein-volk}{here}\index{Theme music}.

\textit{--- Liber magnus est.}

>>>>

\section{Foreword}\label{sec:foreword}

@@

A basic understanding of quantum mechanics \cite{bib:Sakurai94}, quantum optics \cite{bib:GerryKnight05}, quantum computing and quantum information theory \cite{bib:NielsenChuang00}\footnote{Throughout this manuscript we use the Nielsen \& Chuang convention for the pronunciation of `zed' \cite{bib:NielsenChuang00}.\index{Zed}}, and classical networking \cite{bib:TanenbaumNet} are helpful, but not essential, to following our discussion. Some mathematical sections require a basic understanding of the mathematical notation of quantum mechanics. Although the reader without this background ought to be able to nonetheless follow the broader arguments.

@@

The theme music for this work may be found \href{http://soundcloud.com/peter-rohde/wir-sind-ein-volk}{here} \copyright\index{Theme music}\footnote{We use the copyright (\copyright) and trademark (\texttrademark) symbols liberally throughout this text when referring to things where we believe commercial opportunities may exist in the future. The authors do not own copyrights or trademarks to anything in this text.}.
